%% $RCSfile: proj_report_outline.tex,v $
%% $Revision: 1.2 $
%% $Date: 2010/04/23 02:40:16 $
%% $Author: kevin $

\documentclass[11pt
              , a4paper
              , twoside
              , openright
              ]{report}

\usepackage{graphicx,psfig,amsmath,float,epstopdf,multirow,mathtools,changepage,amssymb}
\usepackage[para,online,flushleft]{threeparttable}
\usepackage{float} % lets you have non-floating floats
\usepackage{url} % for typesetting urls
\usepackage{caption}
\usepackage{program}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{algorithm, algpseudocode}
\usepackage{etoolbox}
\usepackage{hhline}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage[font=footnotesize,labelfont=bf]{caption}

\let\bbordermatrix\bordermatrix
\patchcmd{\bbordermatrix}{8.75}{4.75}{}{}
\patchcmd{\bbordermatrix}{\left(}{\left[}{}{}
\patchcmd{\bbordermatrix}{\right)}{\right]}{}{}



\usepackage{float} % lets you have non-floating floats

\usepackage{url} % for typesetting urls

%
%  We don't want figures to float so we define
%
\newfloat{fig}{thp}{lof}[chapter]
\floatname{fig}{Figure}

%% These are standard LaTeX definitions for the document
%%                            
\title{Evolutionary Multi-Objective Optimization for Web Service Location Allocation}
\author{Boxiong Tan}

%% This file can be used for creating a wide range of reports
%%  across various Schools
%%
%% Set up some things, mostly for the front page, for your specific document
%
% Current options are:
%  [ecs|msor]              Which school you are in.
%
%  [mcompsci]  Which degree you are doing
%                          You can also specify any other degree by name
%                          (see below)
%  [font|image]            Use a font or an image for the VUW logo
%                          The font option will only work on ECS systems
%
\usepackage[image,ecs,mcompsci]{vuwproject}

% You should specifiy your supervisor here with
%     \supervisor{Firstname Lastname}
% use \supervisors if there is more than one supervisor
\supervisors{Hui Ma, Yi Mei, Mengjie Zhang}
% Unless you've used the bschonscomp or mcompsci
%  options above use
%   \otherdegree{OTHER DEGREE OR DIPLOMA NAME}
% here to specify degree

% Comment this out if you want the date printed.
\date{}

\begin{document}

% Make the page numbering roman, until after the contents, etc.
\frontmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
With the ever increasing number of functional similar web services being available on the Internet, 
the market competition is becoming intense. 
Web service providers realized that good Quality of Service (QoS) is a key of business success
and low network latency is a critical measurement of good QoS.
Because network latency is related to geometric location,
a straightforward way to reduce network latency is to allocate services to proper locations. 
Hence, it is necessary to provide an effective web services allocation algorithm to WSPs. 
In this project, we model the Web service location allocation 
problem as a multi-objective optimization problem - minimizing overall network latency and total cost. 
We use two PSO-based algorithms with different strategies - an aggregating strategy and a Pareto front 
strategy to solve the problem. We further develop a new PSO-based algorithm with rounding function approach to improve the quality of solutions. 
The result shows that the new algorithm could provide diverse solutions. In addition, the new algorithm has good 
performance regardless of increasing problem size.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\include{acknowledge}

\tableofcontents

% we want a list of the figures we defined
 \listof{fig}{Figures}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\mainmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% individual chapters included here
\include{introduction}
\include{using}
% \include{example}
 \include{conclusion}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\backmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\bibliographystyle{ieeetr}
\bibliographystyle{acm}
\bibliography{sample}


\end{document}
